My Title

### 2022-08-23 misc/collapse cheat sheet/collapse_cheat_sheet.Rnw
Adding footer to cheatsheet, and reorganizing folder a bit.

%% Sets page size and margins
\usepackage[landscape,top=0.5cm,bottom=0.6cm,left=0.5cm,right=0.5cm,marginparwidth=1.75cm]{geometry}

@@

\usepackage{setspace} % \linespread{1.3}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.02em}%Length of space between paragraphs
% \setlength{\columnsep}{6mm}
\setlength{\itemsep}{0.2em}
\pagestyle{empty}

@@

\begin{multicols*}{4}
%\setlength{\premulticols}{1pt}
%\setlength{\postmulticols}{1pt}
%\setlength{\multicolsep}{1pt}
%\setlength{\columnsep}{2pt}

@@

<<>>=
# Population weighted mean (PCGDP, LIFEEX) & mode (country), and sum(POP)
collap(wlddev, country + PCGDP + LIFEEX ~ income, w = ~ POP)
@
%\vspace{-10mm}

% \newpage

% ------------------------------------------------------------------
% Second Page
% ------------------------------------------------------------------

@@

\hrrule
\section{List-Processing}
%\vspace{1mm}
\itxt{Functions to process (nested) lists (of data objects)}\\ [0.5em]
%\setstretch{1.5}
\code{ldepth()} - level of nesting of list\\ [0.5em]
\code{is\_unlistable()} - is list composed of atomic objects\\ [0.5em]
\code{has\_elem()} - search if list contains certain elements\\ [0.5em]
\code{get\_elem()} - pull out elements from list / subset list\\ [0.5em]
\code{atomic\_elem[<-](), list\_elem[<-]()} - get list with atomic /\\ \qquad sub-list elements, examining only first level of list\\ [0.3em]
\code{reg\_elem(), irreg\_elem()} - get full list tree leading to atomic\\ \qquad ('regular') or non-atomic ('irregular') elements\\ [0.5em]
\code{rsplit()} - efficient (recursive) splitting\\ [0.5em]
\code{t\_list()} - efficient list transpose (transpose lists of lists)\\ [0.5em]
\code{rapply2d()} - recursive apply to lists of data objects\\ [0.5em]
\code{unlist2d()} - recursive row-binding to data.frame\\ [0.5em]
%\setstretch{1}

@@

\end{multicols*}
\end{document}

>>>>

%% Sets page size and margins
\usepackage[landscape,top=0.5cm,bottom=-1cm,left=0.5cm,right=0.5cm,marginparwidth=1.75cm]{geometry}

@@

\usepackage{setspace} % \linespread{1.3}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.02em}%Length of space between paragraphs
% \setlength{\columnsep}{6mm}
\setlength{\itemsep}{0.2em}
\pagestyle{empty}
% \usepackage{fancyhdr}
% \rfoot{Page \thepage}

@@

%\begin{adjustbox}{totalheight=0.5\textheight} % -2\baselineskip
% \resizebox*{!}{\textheight}{%
\begin{multicols}{4}
%\setlength{\premulticols}{1pt}
%\setlength{\postmulticols}{1pt}
%\setlength{\multicolsep}{1pt}
%\setlength{\columnsep}{2pt}

@@

<<>>=
# Population weighted mean (PCGDP, LIFEEX) & mode (country), and sum(POP)
collap(wlddev, country + PCGDP + LIFEEX ~ income, w = ~ POP)
@
\end{multicols} % \vspace{-20mm}

% \end{adjustbox}
%}
% \hrrule
\vspace{-5mm}
\textcolor{lightgray}{\hrulefill}\\
{\scriptsize \vspace{-0.5mm}
 Page 1 of 2 \hfill \textcopyright\ Sebastian Krantz\ \textbullet\ Learn more at \href{https://sebkrantz.github.io/collapse/}{sebkrantz.github.io/collapse}\ \textbullet\ Source code at \href{https://github.com/SebKrantz/collapse}{github.com/SebKrantz/collapse}\ \textbullet\ Updates announced at \href{https://twitter.com/collapse\_R}{twitter.com/collapse\_R} - \#rcollapse\ \textbullet\ Cheatsheet created for \emph{collapse} version 1.8.8\ \textbullet\ Updated: 2022-08
}

\newpage

% ------------------------------------------------------------------
% Second Page
% ------------------------------------------------------------------
\begin{multicols}{4}

@@

\hrrule
\section{List Processing}
%\vspace{1mm}
\itxt{Functions to process (nested) lists (of data objects)}\\ [0.5em]
%\setstretch{1.5}
\code{ldepth()} - level of nesting of list\\ [0.5em]
\code{is\_unlistable()} - is list composed of atomic objects\\ [0.5em]
\code{has\_elem()} - search if list contains certain elements\\ [0.5em]
\code{get\_elem()} - pull out elements from list / subset list\\ [0.5em]
\code{atomic\_elem[<-](), list\_elem[<-]()} - get list with atomic /\\ \qquad sub-list elements, examining only first level of list\\ [0.3em]
\code{reg\_elem(), irreg\_elem()} - get full list tree leading to atomic\\ \qquad ('regular') or non-atomic ('irregular') elements\\ [0.5em]
\code{rsplit()} - efficient (recursive) splitting\\ [0.5em]
\code{t\_list()} - efficient list transpose (transpose lists of lists)\\ [0.5em]
\code{rapply2d()} - recursive apply to lists of data objects\\ [0.5em]
\code{unlist2d()} - recursive row-binding to data.frame\\ [0.5em]
%\setstretch{1}

@@

\end{multicols}

\vspace{-5mm}
\textcolor{lightgray}{\hrulefill}\\
{\scriptsize \vspace{-0.5mm}
 Page 2 of 2 \hfill \textcopyright\ Sebastian Krantz\ \textbullet\ Learn more at \href{https://sebkrantz.github.io/collapse/}{sebkrantz.github.io/collapse}\ \textbullet\ Source code at \href{https://github.com/SebKrantz/collapse}{github.com/SebKrantz/collapse}\ \textbullet\ Updates announced at \href{https://twitter.com/collapse\_R}{twitter.com/collapse\_R} - \#rcollapse\ \textbullet\ Cheatsheet created for \emph{collapse} version 1.8.8\ \textbullet\ Updated: 2022-08
}

\end{document}
